An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-11-20 article.tex
backup

XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoosted trees are a boosted tree ensemble method that can be used to classify classes, or predict continuous response variables. They were chosen for this analysis as the data contained a mixture of class and continuous variables. Moreover, XGBoosted trees are unaffected by multicollinearity, and offer high predictive performance for a wide variety of purposes \citep{chenXGBoostScalableTree2016}.

@@

As there were multiple different loss functions, multiple different forms of validation were used. In each case the data was split into training data, which constituted 80\% of the original data. The remaining 20\% was used in testing and validation. Data was stratified when splitting the data into these subsets to conserve the same proportion of class occurrences between training, testing and validation data. For continuous variables 20\% was used as testing data, minimising the root-mean-square function. The final model was validated using repeated k-fold cross validation for 10 folds, repeated 10 times. $R^2$ scores were used to determine the best regression models during validation.
For binary and multiclass variables, data was split into 80\% training, 10\% testing and 10\% validation data. For class variables, validation was summarised through the accuracy, the proportion of true negatives and positives.
\par
The XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. This allowed us to utilise cross validated grid search functions when selecting for better performing hyperparameters. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

\subsection{Surrogate Models}

The creation of more interpretable models such as linear regression in parallel to AI systems has been used to explain variable's relationships within black box algorithms \citep{molnarInterpretableMachineLearning2022}. As XGBoost create an ensemble of decision trees, here we use classification and regression trees to gain insight into intricacies of the ensembles derived through XGBoost. Decision Trees were created for operating costs, revenue and region. These models describe the partitions that are useful in predicting these variables; giving insight into the trees that make up the ensembles created by XGBoost. These trees were created using the rparts and caret packages \citep{kuhnBuildingPredictiveModels2008,terrytherneauRpartRecursivePartitioning2022} in the R statistical programming language \citep{rcoreteamLanguageEnvironmentStatistical2021}.
\par
Decision trees were validated using K-fold cross validation. Each model was validated using 10 folds, utilising a random selection of different samples ten separate times to validate each of the decision trees. The same measure of accuracy as the XGBoosted trees was used for comparison.

@@

We investigated the link between revenue to other variables in the SWA data by predicting it, and then linking each variable to revenue through variable importance. The prediction of revenue performed similarly to operating cost achieving an $R^2$ of 0.7716 (with a standard deviation of 0.1525). A regression tree was used as a surrogate model to present an example of the typical type of decision tree present within the XGBoost Ensemble, however the surrogate model only achieved an $R^2$ of 0.0961 (with a standard deviation of 0.0181) and the XGBoosted ensemble.
\par
The important variables when attempting to determine revenue were size, yield, fuel and water (see \ref{fig:revenue_sankey}). Due to regions being recorded separately for importance none appeared as the most important variables, overall regions contributed to 234 nodes in the ensemble making them collectively the third most important variable. Although performing poorly, the surrogate model highlights the importance of size in determining revenue. Area also appearing as a variable of higher importance is show to be highly interrelated with other variables. The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

@@

The relationships to operating cost through variable importance were found to be similar to that of revenue. With fuel, water, area and yield occurring the most (see figure \ref{fig:operating_costs_sankey}). A surprising difference is that the most important operational consideration for operating cost is the use of fungicide, compared to revenue where slashing is the most important (comparing Figure \ref{fig:region_sankey} and \ref{fig:operating_costs_sankey}). The variables that feed into these decisions are also very differing with diesel being the most informative to slashing and area being the most informative to the need for fungicide.
\par
Again, region played a determining factor overall but not as much individually with region contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
Comparatively to revenue, operating cost performed better The XGBoosted regression ensemble achieved an $R^2$ of 0.8025 (with a standard deviation of 0.1033). Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).

@@

When considered overall, Region was a highly informative variable through measure of importance to both operating cost and revenue. Notably the overall importance of region to revenue was 234 (making it the third most important variable when considerng all regions together). The Barossa Valley region and Tasmania were the two most important regions in relation to revenue; these two regions are considered to be some of the highest revenue per hectare regions in Australia \citep{wineaustraliaNationalVintageReport2022}. These two regions are also relative opposites in winegrowing climates with the Barossa being warm and dry climate focussing on Shiraz grapes and Tasmania being a cool wet climate that grows Pinot. 
\par
When considering all regions together, it had the most node contributions to determining operating costs with an importance of 334. Of all the regions, again Tasmania was the most important, followed by the Adelaide Hills. In contrast to revenue, both climates are considered cool and wet, and warmer drier regions such as the Barossa and Hunter Valley only contributed roughly half the same number of nodes to the ensemble. When looking at \ref{fig:region_sankey} the inclusion of slashing and fungicide spraying is the likely reason; with fungal and weed pressure being greater in cooler wetter regions.
\par
Both diesel and petrol were of more relative importance in operating costs than water was compared with region. similar to those used to classify region (see Figure \ref{fig:region_sankey}, except water used. The surrogate model relied heavily on the use of water source to classify regions, which is reflective of regional access to resources being a deciding factor in vineyard management (see Figure \ref{fig:region_tree}). A major difference between region and revenue was the importance given to water use, with water use being a relatively more important variable in predicting region than revenue (considering its rank in importance to other variables). 
\par
The surrogate model for region performed better than other surrogate models with 32.34\% (3.67\% standard deviation). The prominence of types and use of water resources was in classifying region is reflective of difference of availability of water resources is when comparing different regions (see Figure \ref{fig:region_tree}). The XGBoost ensemble, did not perform as well as operating costs or revenue with 56.82\% accuracy (50.58\% validation accuracy). The difference in accuracy is in part due to the large number of classes (being 58). The ensemble did not differ greately from the surrogate model, with a continuing emphasis on Area, water, fuel and yield as determining factors (see Figure (\ref{fig:region_sankey}). 
% Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
Many of the regions had significantly lower reporting rates, resulting in much poorer classification performance. The regions with the most samples performed the best. Bordering regions were routinely grouped together and misclassified as the same region. Two areas that suffered the most from this, specifically with the classification tree were the Limestone Coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling. The classification tree likely had more difficulty discerning vineyards closer to the river using only water sources due to the greater access to river water in these areas.

@@

The explored relationships between vineyard resource use, operations and geographical properties to revenue and operating costs highlight how decisive regional influences can be determining a vineyard's economic outcomes. Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}.

@@

In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region. Where, the need to pressurise irrigation systems from river water or to generate power would require larger amounts of diesel and petrol.

@@

Operational costs showed similar importance across fuel, water and tractor use. The dominating factor of area likely played a large part in determining how costly a tractor pass would be, or in defining the ratio of water applied to the amount of vines. The node frequency was high for area but much lower in general across the other variables, which could indicate the need to be more circumstantial in determining operational costs. Although it was attempted to capture the complexity between how variables interacted when determining operational costs (see Figure \ref{fig:operating_costs_sankey}), it is likely yet more complicated. An example of how interrelated operational costs can be, is 

@@

When determining revenue, similar variables were used to operational cost; with region also being of high variable importance relative to other variables (when considering all regions together in importance). It is difficult to extrapolate the specific influence of location on a vineyard's outcomes due to the broad and varying definition of a region. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation in one way, as it is too broad to fully capture a vineyards location and how that influences variables at a more granular level. However, as buyers set prices at regional levels, it is still important to consider a vineyards Geographical Indicator region. 

@@

Decisions made on the ground have far-reaching effects and are difficult to completely capture. A higher number of tractor passes used as a preventative measure for occurrences such as disease, may incur higher operational costs but could be critical in preventing long term losses. With factors such as erosion and soil health being difficult to capture but also influenced by tractor use \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020}. Although, performing well in $R^2$, the ability to predict operational costs is limited by the variables incorporated. Reductions in fuel, water and tractor use are obvious methods to reduce operational costs but not necessarily achievable decisions. Without fully capturing more granular activities such as the specifics of what fuel was used for, it is hard to determine what decisions specifically influence the operational costs. Electricity in particular is used predominantly for irrigation. Size is also a further consideration where slashing and spraying are measured in discrete tractor passes and show a surprising connection to the overall size of a vineyard, despite not being scaled to any measure of size. This would mean that, although measured as the same increment, a slashing or spraying pass in a larger vineyard would consume more fuel and wages than in a smaller vineyard.

@@

A more granular definition of region may help to better discern the differences in practices, and the reason for employing them. More sophisticated models, specifically those that utilise expert opinion, may also help to capture and address the decision-making process. An example is the optimisation of fungicide sprays using Bayesian models that forecast disease risk \citep{luDiseaseRiskForecasting2020}. 

@@

Separately revenue and operating cost did have a greater predictability than their counterpart profit. The disparity in accuracy between profit and other economic outcomes is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on decisions made and chance. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

@@

This study has provided valuable insights into the multifaceted dynamics governing operational costs and revenue. The impact of different regions highlighted the complex interrelatedness of variables within a vineyard. We relate how factors such as water and fuel intersect to impact operational costs and how different seasonal events affect these operations; as well as the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. Further work could pursue causal models and the creation of decision support systems. It is difficult to untangle the predictive and correlative nature of a variable compared to the causal reasons. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs and enhancing sustainability.

>>>>

XGBoosted (eXtreme Gradient Boosting) trees, described in more detail below,  were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoosted trees are a boosted tree ensemble method that can be used to classify classes, or predict continuous response variables. They were chosen for this analysis as the data contained a mixture of class and continuous variables. Moreover, XGBoosted trees are unaffected by multicollinearity, and offer high predictive performance for a wide variety of purposes \citep{chenXGBoostScalableTree2016}.

@@

For each model the data was split into training data, which constituted 80\% of the original data. The remaining 20\% was used in testing and validation. Categorical data was stratified to conserve the same proportion of class occurrences between training, testing and validation data. For continuous variables 20\% was used as testing data and the models were validated using 10 repetitions of the sampling process (10-fold cross validation). $R^2$ scores were used to determine the best regression models during validation. $R^2$ was used instead of RMSE to avoid the issue of comparing models of different units to each other when considering how well each model extrapolated to further data. For binary and multiclass variables, validation was summarised through the accuracy, the proportion of true negatives and positives.
\par
The XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. This allowed us to utilise cross validated grid search functions when selecting for better performing hyperparameters. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

% \subsection{Surrogate Models}

% The creation of more interpretable models such as linear regression in parallel to AI systems has been used to explain variable's relationships within black box algorithms \citep{molnarInterpretableMachineLearning2022}. As XGBoost create an ensemble of decision trees, here we use classification and regression trees to gain insight into intricacies of the ensembles derived through XGBoost. Decision Trees were created for operating costs, revenue and region. These models describe the partitions that are useful in predicting these variables; giving insight into the trees that make up the ensembles created by XGBoost. These trees were created using the rparts and caret packages \citep{kuhnBuildingPredictiveModels2008,terrytherneauRpartRecursivePartitioning2022} in the R statistical programming language \citep{rcoreteamLanguageEnvironmentStatistical2021}.
% \par
% Decision trees were validated using K-fold cross validation. Each model was validated using 10 folds, utilising a random selection of different samples ten separate times to validate each of the decision trees. The same measure of accuracy as the XGBoosted trees was used for comparison.

@@

The prediction of revenue performed similarly to operating cost achieving an $R^2$ of 0.7716 (with a standard deviation of 0.1525). The value of predictors' relative importance was then calculated through the number of nodes used within the XGBoost. Values for relative importance were then used to construct Sankey and Chord diagrams to compare the contribution of each variable to predicting revenue.
\par
In order of importance, predictors of revenue were fuel use(petrol 307 and diesel 144), yield (285), size (216) and water use (199). Here, the values in the brackets indicate the relative importance of each variable (see \ref{fig:revenue_sankey}). Overall regions contributed to 234 nodes in the ensemble making them collectively the third most important variable. The chord diagram illustrates that vineyard area is also of high relative importance to other variables especially slashing. The overall importance of area to other variables is evident by its larger circumference within the chord diagram (see B in Figure \ref{fig:revenue_sankey}).
% The strong relationship of vineyard area to revenue and its predictors  but also has a high relative importance to the other predictors, The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

@@

Comparatively to revenue, operating cost performed better with the XGBoosted regression ensemble achieving an $R^2$ of 0.8025 (with a standard deviation of 0.1033). The relationships to operating cost through variable importance were found to be similar to that of revenue, with fuel, water, area and yield having the largest number relative importance (see figure \ref{fig:operating_costs_sankey}). A surprising difference is that the most important operational consideration for operating cost is the use of fungicide, compared to revenue where slashing is the most important (comparing Figure \ref{fig:region_sankey}). The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).

@@

When considered overall, Region was a highly informative variable based on measures of importance for both operating cost and revenue. As noted above, Region was the third most important variable for determining revenue. The Barossa Valley region and Tasmania were the two most important regions in relation to revenue; these two regions are considered to be some of the highest revenue per hectare regions in Australia \citep{wineaustraliaNationalVintageReport2022}. These two regions are also relative opposites in winegrowing climates with the Barossa having a warm and dry climate focussing on Shiraz grapes and Tasmania having a cool wet climate that favours Pinot. 
\par
As also noted above Region was also a key determinant of operating costs. Again Tasmania was the most important, followed by the Adelaide Hills. In contrast to revenue, both climates are considered cool and wet, and warmer drier regions such as the Barossa and Hunter Valley only contributed roughly half the same number of nodes to the ensemble. Based on further analysis of Regions (Figure \ref{fig:region_sankey}) the inclusion of slashing and fungicide spraying is the likely reason with fungal and weed pressure being greater in cooler wetter regions.
\par
The XGBoost ensemble, did not perform well when predicting operating costs or revenue with 56.82\% accuracy (50.58\% validation accuracy). The difference in accuracy is in part due to the large number of classes (58 regions). The ensemble had a great emphasis on area, water, fuel and yield as determining factors (see Figure (\ref{fig:region_sankey}). 
% Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
Many of the regions had significantly lower reporting rates, resulting in much poorer classification performance. The regions with the most samples performed the best. Bordering regions were routinely grouped together and misclassified as the same region. Two areas that suffered the most from this were the Limestone Coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling.

@@

This study has explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs

geographical regions with respect to a vineyards revenue and operating costs. The analysis was based on a large national study of XXX

Three main findings were identified. First, the most important predicted of revenue were XXX

With YYY showing the relationships among the corresponding set of predictor variables

Second XXX for operating cost

Third for regions...

highlight how decisive regional influences can be determining a vineyard's economic outcomes. 
Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}.

@@

In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel to pressurise their irrigation systems.

@@

Operational costs showed similar importance across fuel, water and tractor use. The dominating factor of area likely played a large part in determining how costly a tractor pass would be, or in defining the ratio of water applied to the amount of vines. The node frequency was high for area but much lower in general across the other variables, which could indicate the need to be specific when attempting to determine the cause of a operational cost. Although it was attempted to capture the complexity between how variables interacted when determining operational costs (see Figure \ref{fig:operating_costs_sankey}), it is likely yet more complicated. An example of how interrelated operational costs can be, is 

@@

When determining revenue, similar variables were used to operational cost; with region also being of high variable importance relative to other variables (when considering all regions together in importance). It is difficult to extrapolate the specific influence of location on a vineyard's outcomes due to the broad and varying definition of a region. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation in one way, as it is too broad to fully capture a vineyards location and how that influences variables at a more granular level. However, as buyers set prices at regional levels, it is still important to consider this factor. 

@@

Decisions made on the ground have far-reaching effects and are difficult to completely capture. A larger number of tractor passes used as a preventative measure for occurrences such as disease may incur higher operational costs but could be critical in preventing long term losses. Although the models demonstrated a good predictive fit (via large $R^2$ values), the ability to predict operational costs is limited by the variables incorporated in the analysis. Other factors such as erosion and soil health are also influenced by tractor use and would contribute to these operational costs but are difficult to measure and were not available as part of the data \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020}. Reductions in fuel, water and tractor use are obvious methods to reduce operational costs but not necessarily achievable decisions. Without fully capturing more granular activities for example the specific reasons for fuel use, it is difficult to determine what decisions specifically influence the operational costs.
%  Electricity in particular is used predominantly for irrigation. 
% Size is also a further consideration where slashing and spraying are measured in discrete tractor passes and show a surprising connection to the overall size of a vineyard, despite not being scaled to any measure of size. This would mean that, although measured as the same increment, a slashing or spraying pass in a larger vineyard would consume more fuel and wages than in a smaller vineyard.

@@

% A more granular definition of region may help to better discern the differences in practices, and the reason for employing them. 
More sophisticated models, specifically those that utilise expert opinion, may also help to capture and address the decision-making process. An example is the optimisation of fungicide sprays using Bayesian models that forecast disease risk \citep{luDiseaseRiskForecasting2020}. 

@@

Separately revenue and operating cost did have a greater predictability than their counterpart profit. The disparity in accuracy between profit and other economic outcomes is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on predictable factors unforecasted factors, farming practice and farmers' decisions. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

@@

This study has provided valuable insights into the multifaceted dynamics governing operational costs and revenue. The impact of different regions highlighted the complex interrelatedness of variables within a vineyard. We relate how factors such as water and fuel intersect to impact operational costs and how different seasonal events affect these operations; as well as the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. Further work could pursue causal models and the creation of decision support systems. It is difficult to untangle the predictive and correlative nature of a variable compared to the causal reasons. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs, increasing revenue and enhancing sustainability.
